Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Comments k=2

@@

\end{proof}

>>>>

	\maciek{Proposition 1: For $\lambda=\alpha$ the algorithm \RM is strictly 6-competitive.	Proposition 2: "The algorithm \RM is strictly 6-competitive for $\lambda=\alpha$.	"?}

\maciek{First the intuitions, then the theorem, and right after the proof?}

\maciek{The first sentence of the proof: first parenthesis does not explain things better, can be omitted. The second parenthesis also, I think: we use swap a lot all over the paper, and it should be understandable at the last proof.}

\maciek{by collocating multiple pairs at once. "by collocating \textbf{two} pairs at once"}

\maciek{"before they inflict too much cost" Unnecessary? Just collocating is enough.}

\maciek{"Therefore it pays a cost of 1 migration per pair". I am confused by this sentence. Charging one is ok, but payment is always the same. Maybe it will become clear with the pic}

\maciek{"a cost inflicted by a pair" the cost?}

\maciek{"incurs the cost some time since" Maybe a different word than some? It is unclear if we refer to interval or a specific moment.}

@@

\end{proof}
\maciek{Fonts of OPT and \OPT differ. The latter is better.}

\maciek{Excessive comma before ", is $\lambda +2\alpha$?}

\maciek{m not introduced as the end of time in the proof, and also used in the intuitions. Consider some other symbol like $\tau$ or $t_F$}

\maciek{"then \OPT pays $\lambda$ for serving" comma before then?}

\maciek{", or $\alpha$ for collocating \textbf{and serving some requests remotely}" remove what's bold? The migration is sufficient}

\maciek{"it can have one edge already collocated" at most one edge?}

\maciek{"at the same time. However" One sentence? joined with "but"}

\maciek{"similarly as in the former" "\textbf{similarly to the former}"}

\maciek{"this means," "\textbf{this means that}"}

\maciek{Suggestion: maybe call "its intervals" "\textbf{the saturating intervals}"?}
